Descriptive characteristics of Long COVID Cohorts

### 2022-10-28 characterisation/Code/Comparing_symptoms.Rmd
update

---
title: "Exploring_symptoms_across_cohorts"
output: html_document
---

@@

# get data for table 1
load(here("data", "table1_data_new_infections.Rda"))

@@

# variables
vars<-c(
        "age",
        "age_gr2",
        "gender",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment"
)

factor.vars<- c(
        "age_gr2",
        "gender",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment"
)

@@

>>>>

---
title: "Descriptive characteristics of Long COVID Cohorts"
output: html_document
---

@@

# get data for table 1
load(here("data", "table1_data.Rdata"))

@@

# variables
vars<-c(
        "age",
        "age_gr2",
        "gender",
        "trimester",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment"
)

factor.vars<- c(
        "age_gr2",
        "gender",
                "trimester",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment"
)

@@

```{r include=FALSE}
table2.data<-rbind(  
# those without missing values
       table1_data_tested_negative   %>%
        mutate(group = "1- Tested negative"),
       table1_data_tested_negative   %>%
        filter(long_covid == 1)%>%
          mutate(group = "2- Long Covid symptoms (90 days)"))

# variables
vars<-c(
        "age",
        "age_gr2",
        "gender",
        "trimester",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment"
)

factor.vars<- c(
        "age_gr2",
        "gender",
                "trimester",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment"
)

summary.characteristics.negative <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table2.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 1,
  printToggle=FALSE)

## Table: Baseline characteristics of individuals tested negative and with long COVID-18 symptoms
```{r}

kable(summary.characteristics.negative, 
      col.names = c("Tested negative, earliest",  
                    "Long COVID-19 symptoms, 90 days",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)

```{r include=FALSE}
table3.data<-rbind(  
# those without missing values
        table1_data_new_infections  %>%
        mutate(group = "New infections"),
        table1_data_tested_negative   %>%
        mutate(group = "Tested negative"))

# variables
vars<-c(
        "age",
        "age_gr2",
        "gender",
        "trimester",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment",
                "long_covid"

)

factor.vars<- c(
        "age_gr2",
        "gender",
                "trimester",
        "nationality_cat",
        "vaccination_status",
        "medea",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment",
        "long_covid"
)

summary.characteristics.infection.negative <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table3.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 1,
  printToggle=FALSE)

## Table: Baseline characteristics of individuals tested negative and with long COVID-18 symptoms
```{r}

kable(summary.characteristics.infection.negative, 
      col.names = c("New COVID-19 infection",  
                    "Tested negative",
                    "SMD"
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)
